Autonomous Oceanographic Data Collection. Learning Excursion Sets of Vector-valued Gaussian Random Fields \\\vspace{5mm} Authors response to 2$^{nd}$ review \\\vspace{5mm} \small{Manuscript: AOAS1910-027}

### 2021-01-04 ans_to_reviewers/ans-to-2nd-rev.tex
Updates from Overleaf

\vspace{5mm}
\noindent \aecom \textbf{1}:

Bla bla bla.

>>>>

\vspace{5mm}
\noindent \aecom \textbf{1 - Reply to AE comment 4}: 
T hank you for explaining the sampling limitations to me in your reply.  However, I think these limitations should also be noted in the narrative, and the sub-optimality of the resulting trajectory should be acknowledged.

\vspace{5mm}
\noindent \aecom \textbf{2 - Page 2, line 15}:  I think it would be more appropriate to refer to this as sampling design rather than sampling.

\vspace{5mm}
\noindent \aecom \textbf{3 - Page 4, line 3}:  Replace “proxys” with the correct plural “proxies”

\vspace{5mm}
\noindent \aecom \textbf{4 - Page 5, line 16:}  Change  “the  PhD  thesis  (Stroh,  2018,  p.  82)”  to ”Stroh (2018, p. 82)”

\vspace{5mm}
\noindent \aecom \textbf{5 - Page 22, line 8:}  From Figure 9(c), the nugget effect in the empirical variogram appears to be approximately 0.4 for salinity and 0.7 for temperature.  Even if the sensor specifications were essentially 0, it would be a stretch to say that a variance of 0.0625 was a “middle ground” between the empirical nugget effect and the sensor specifications.  So either give a better justification of your choice of 0.0625 or, if that’snot possible, then redo the analysis with a more justifiable choice.

\vspace{5mm}
\noindent \aecom \textbf{6 - Page 22, line 5:}  Insert “triangular” immediately after “equilateral”
